### 2020-03-24 README.Rmd
Update root README

![GitHub last commit](https://img.shields.io/github/last-commit/csdaw/candidaev.svg?style=popout)

@@

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2019) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins". 
version x.x.x. Zenodo. URL.

>>>>

@@

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2020) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, submitted.

@@

> Dawson, C. S., Garcia-Ceron, D.,. Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2020) Research compendium for "Protein markers for 
_Candida albicans_ EVs include claudin-like Sur7 family proteins". 
version x.x.x. Zenodo. URL.
